Blum axioms and nondeterministic computation of functions

### 2016-05-19 paper.tex
paper.tex: Improve the wording a bit.

This paper presents several attempts to establish
how a nondeterministic Turing machine could compute a function,
and to extend the concept of ``polynomial-time computable'' under each definition.
Section~\ref{sec:our-approach} sets reasonableness criteria
to both the definition of function computation and complexity of the computation.
Section~\ref{sec:nondeterministic_computation_of_functions},
which contains the several definitions,
presents and criticizes Hopcroft and Ullman's and Goldreich's definitions
(sections \ref{sec:hopcroft-ullman} and~\ref{sec:goldreich}),
proposes one possible definition that meet the quality standards
(section~\ref{sec:proposed}),
and shows other two definitions,
by Krentel (sec~\ref{sec:krentel}) and Valiant (sec~\ref{sec:valiant}),
that, altough were not proposed in the context
of general nondeterministic computation of functions,
also meet the quality standards and sidesteps the problems with the proposed definition
(presented in section~\ref{sec:np-completeness-extension}).
The development of this project is mentioned in section~\ref{sec:development},
after the concluding remarks (section~\ref{sec:conclusion}).

@@

Sections \ref{sec:godel-numberings} and~\ref{sec:blum-axioms}
introduced the concept of acceptable Gödel numbering,
the Blum axioms,
and its complexity classes.
As we want to regard these concepts as ``quality requirements''
for the definitions,
we will analyze each of them to see whether they define acceptable Gödel numberings,
the analogous time complexity satisfies Blum axioms,
and that the characteristic function\footnotemark{} of the Boolean satisfiability problem
can be solved in ``polynomial time'' according to that complexity measure.
\footnotetext{
    The characteristic function of a set $A$
    is the function $1_A$ defined to be $1$ for $x \in A$
    and $0$ for $x \notin A$.
}
(This last one is an indicative that
the definition preserves the exponential speed-up that nondeterminism gives to deciders.)

>>>>

This paper presents several attempts to establish
how a nondeterministic Turing machine could compute a function,
and to extend the concept of ``polynomial-time computable'' under each definition.
Section~\ref{sec:our-approach} sets reasonableness criteria
to both the definition of function computation and complexity of the computation.
Section~\ref{sec:nondeterministic_computation_of_functions},
which contains the several definitions,
presents and criticizes Hopcroft and Ullman's and Goldreich's definitions
(sections \ref{sec:hopcroft-ullman} and~\ref{sec:goldreich}),
proposes one possible definition that meet the quality standards
(section~\ref{sec:proposed}),
and shows other two definitions,
by Krentel (section~\ref{sec:krentel}) and Valiant (section~\ref{sec:valiant}),
that, altough were not proposed in the context
of general nondeterministic computation of functions,
also meet the quality standards and sidesteps the problems with the proposed definition
(presented in section~\ref{sec:np-completeness-extension}).
The development of this project is mentioned in section~\ref{sec:development},
after the concluding remarks (section~\ref{sec:conclusion}).

@@

Sections \ref{sec:godel-numberings} and~\ref{sec:blum-axioms}
introduced the concept of acceptable Gödel numbering,
the Blum axioms,
and its complexity classes.
As we want to regard these concepts as ``quality requirements''
for the definitions,
we will analyze each of them to see whether they define acceptable Gödel numberings,
the analogous time complexity satisfies Blum axioms,
and that the characteristic function\footnotemark{} of the Boolean satisfiability problem
can be solved in ``polynomial time'' according to that complexity measure.
\footnotetext{
    The characteristic function of a set $A$
    is the function $1_A$ defined to be $1$ for $x \in A$
    and $0$ for $x \notin A$.
}
(This last requirement expresses that
the definition preserves the exponential speed-up that nondeterminism gives to deciders.)
